Model LF

### 2022-11-21 max_dp endogen stød.Rmd
Commit

  shock_1_model  = TIMESERIES(c(shock_1_model ),   
                           START=c(2005,2),FREQ=4),
  shock_2_model  = TIMESERIES(c(shock_2_model ),   
                           START=c(2005,2),FREQ=4),
  shock_3_model  = TIMESERIES(c(shock_3_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
   pf_shock = TIMESERIES(c(pf_shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
  pm_ds_shock = TIMESERIES(c(pm_ds_shock),   
                        START=c(2005,2),FREQ=4),
  iloan_shock = TIMESERIES(c(iloan_shock),   
                        START=c(2005,2),FREQ=4),
  idep_shock = TIMESERIES(c(idep_shock),   
                        START=c(2005,2),FREQ=4),
   ibd_shock = TIMESERIES(c(ibd_shock),   
                        START=c(2005,2),FREQ=4),
  iboa_shock = TIMESERIES(c(iboa_shock),   
                        START=c(2005,2),FREQ=4),
   tax_rate1_shock = TIMESERIES(c(tax_rate1_shock),   
                        START=c(2005,2),FREQ=4),
  wage_gap = TIMESERIES(c(wage_gap),   
                        START=c(2006,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
  wage_ds_tt = TIMESERIES(c(wage_ds_tt),   
                        START=c(2006,1),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4),
   kont_h_ratio = TIMESERIES(c(kont_h_dp_person),   
                        START=c(2005,2),FREQ=4),
     kont_h = TIMESERIES(c(kont_h),   
                        START=c(2005,2),FREQ=4),
    prod_ds_shock = TIMESERIES(c(prod_ds),   
                        START=c(2005,2),FREQ=4),
  d_2007q4 = TIMESERIES(c(d_2007q4),   
                        START=c(2005,2),FREQ=4),
  lf_test = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  shock_lf_model = TIMESERIES(c(shock_lf_model),   
                        START=c(2005,2),FREQ=4),
  emp_old = TIMESERIES(c(emp),   
                        START=c(2005,2),FREQ=4),
  emp_sens = TIMESERIES(c(emp),   
                        START=c(2005,2),FREQ=4),
   prod_ds_sens = TIMESERIES(c(prod_ds),   
                        START=c(2005,2),FREQ=4)
)
```

@@

```{r}
plot(prod_bs3, col= "green"); lines(prod, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(ur_ds_bs3, col= "green"); lines(ur_ds, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(ur_bs3, col= "green"); lines(ur, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(emp_bs3, col= "green"); lines(emp, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(prod_bs3, col= "green"); lines(prod_ds_shock_bs3, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()
```

@@

## Baseline Scenario 5-6

@@

## Baseline Scenario 5b

@@

## Baseline Scenario 7

@@

```{r}
plot(part_000, col= "red"); lines(part_bs1, col = "blue");
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("red", "blue")); 
grid()
```
```{r}

plot(((lf_000 - lf_bs1)*1000), col= "black", xlab= "Year", ylab= "% Change in gdp");
legend("top", legend=c("GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()
```

@@

```{r}
plot(part_01, col= "red"); lines(part_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(pc_ds_01, col= "red"); lines(pc_ds_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(nben_h_01, col= "red"); lines(nben_h_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_ds_t_01, col= "red"); lines(wage_ds_t_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(komp_r_01, col= "red"); lines(komp_r_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(dp_person_01, col= "red"); lines(dp_person_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(kont_h_ratio_01, col= "red"); lines(kont_h_ratio_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_gap1_01, col= "red"); lines(wage_gap1_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(prod_01, col= "red"); lines(prod_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

yk_ds_02 = Shock_2$simulation$yk_ds
emp_02 = Shock_2$simulation$emp
wage_ds_02 = Shock_2$simulation$wage_ds
ur_ds_02 = Shock_2$simulation$ur_ds
pc_ds_02 = Shock_2$simulation$pc_ds
yd_hk_ds_02 = Shock_2$simulation$yd_hk_ds
pconk_ds_02 = Shock_2$simulation$pconk_ds
komp_r_02 = Shock_2$simulation$komp_r
max_dp_02 = Shock_2$simulation$max_dp
nben_h_02 = Shock_2$simulation$nben_h
yd_hk_ds_02 = Shock_2$simulation$yd_hk_ds
ik_02 = Shock_2$simulation$ik
wage_ds_t_02 = Shock_2$simulation$wage_ds_t
nben_h_un_02 = Shock_2$simulation$nben_h_un
nl_g_02 = Shock_2$simulation$nl_g
nsben_h_02 = Shock_2$simulation$nsben_h
dp_person_02 = Shock_2$simulation$dp_person
xk_ds_02 = Shock_2$simulation$xk_ds
mk_ds_02 = Shock_2$simulation$mk_ds
ik_02 = Shock_2$simulation$ik
rer_02 = Shock_2$simulation$rer
ps_ds_02 = Shock_2$simulation$ps_ds
i_bd_nfc_k_ds_02 = Shock_2$simulation$i_bd_nfc_k_ds
yd1_hk_ds_02 = Shock_2$simulation$yd1_hk_ds
yd2a_hk_ds_02 = Shock_2$simulation$yd2a_hk_ds
yd2b_hk_02 = Shock_2$simulation$yd2b_hk

i_equip_nfc_k_ds_02 = Shock_2$simulation$i_equip_nfc_k_ds
u_ds_02 = Shock_2$simulation$u_ds
wage_gap1_02 = Shock_2$simulation$wage_gap1
gk_02 = Shock_2$simulation$gk
kont_h_ratio_02 = Shock_2$simulation$kont_h_ratio
lf_02 = Shock_2$simulation$lf
wage_gap_02 = Shock_2$simulation$wage_gap
max_gap_02 = Shock_2$simulation$max_gap
unemp_02 = Shock_2$simulation$unemp
inflation_02 = Shock_2$simulation$inflation
prod_02 = Shock_2$simulation$prod
net_balance_02 = xk_ds_02 - mk_ds_02

net_balance_02_ratio= (xk_ds_02 - mk_ds_02)/yk_ds_02

ik_ratio_02 = ik_02/yk_ds_02
c_ratio_02 = pconk_ds_02/yk_ds_02

```{r}
plot(max_dp_02, col= "red"); lines(max_dp_bs2, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(i_bd_nfc_k_ds_02, col= "red"); lines(i_bd_nfc_k_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(dp_person_02, col= "red"); lines(dp_person_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(yk_ds_02, col= "red"); lines(yk_ds_bs2, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_ds_t_02, col= "red"); lines(wage_ds_t_bs2, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(i_equip_nfc_k_ds_02, col= "red"); lines(i_equip_nfc_k_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(ps_ds_02, col= "red"); lines(ps_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(yd1_hk_ds_02, col= "red"); lines(yd1_hk_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(pconk_ds_02, col= "red"); lines(pconk_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(gk_02, col= "red"); lines(gk_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(u_ds_02, col= "red"); lines(u_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_gap1_02, col= "red"); lines(wage_gap1_01, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_gap_02, col= "red"); lines(wage_gap_bs2, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(prod_02, col= "red"); lines(prod_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_ds_02, col= "red"); lines(wage_ds_bs2, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

@@

**Ratios**

plot(((c_ratio_02 - c_ratio_bs2)), col= "black", xlab= "Year", ylab= "% Change in consumption", main= "Consumption");
grid()

plot(((ik_ratio_02 - ik_ratio_bs2)), col= "black", xlab= "Year", ylab= "% Change in investments", main= "Investment");
grid()
```

plot(((net_balance_02_ratio - net_balance_bs2_ratio)), col= "black", xlab= "Year", ylab= "change in net exports as percentage of BNP", main= "Net-export");
grid()

plot(((yk_ds_02 - yk_ds_bs2)/yk_ds_bs2), col= "black", xlab= "Year", ylab= "% Change in BNP", main= "BNP");
grid()
```

@@

```{r}
plot((unemp_02-unemp_bs2)*1000, col= "red")

plot((lf_02-lf_bs2)*1000, col= "red")

plot((ur_ds_02-ur_ds_bs2)*1000, col= "red")
plot((pc_ds_02-pc_ds_bs2), col= "red")
```

@@

pr_change_wage_ds_02/pr_change_komp_r_02

pr_change_unemp_02/pr_change_komp_r_02
```

@@

```{r}
# Define add-factor list (defining shock)
constantAdjList_3 <- list(

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

plot(yk_ds_03, col= "red"); lines(yk_ds_bs3, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_ds_t_03, col= "red"); lines(wage_ds_t_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(ur_ds_03, col= "red"); lines(ur_ds_bs3, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(part1_03, col= "red"); lines(part1_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(emp_03, col= "red"); lines(emp_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(komp_r_03, col= "red"); lines(komp_r_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(u_ds_03, col= "red"); lines(u_ds_02, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(prod_03, col= "red", main= "Productivity", ylab= "Productivity (level)"); lines(prod_bs3, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

plot(dp_person_04, col= "red"); lines(dp_person_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(yk_ds_04, col= "red"); lines(yk_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_ds_t_04, col= "red"); lines(wage_ds_t_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(ur_ds_04, col= "red"); lines(ur_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(part1_04, col= "red"); lines(part1_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(emp_04, col= "red"); lines(emp_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(komp_r_04, col= "red"); lines(komp_r_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(u_ds_04, col= "red"); lines(u_ds_02, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(kont_h_ratio_04, col= "red"); lines(kont_h_ratio_02, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

## Scenario 5 reg all

@@

yk_ds_05 = Shock_5$simulation$yk_ds
emp_05 = Shock_5$simulation$emp
wage_ds_05= Shock_5$simulation$wage_ds
ur_ds_05 = Shock_5$simulation$ur_ds
pc_ds_05 = Shock_5$simulation$pc_ds
yd_hk_ds_05 = Shock_5$simulation$yd_hk_ds
pconk_ds_05 = Shock_5$simulation$pconk_ds
komp_r_05 = Shock_5$simulation$komp_r
max_dp_05 = Shock_5$simulation$max_dp
nben_h_05 = Shock_5$simulation$nben_h
yd_hk_ds_05 = Shock_5$simulation$yd_hk_ds
ik_05 = Shock_5$simulation$ik
wage_ds_t_05 = Shock_5$simulation$wage_ds_t
nben_h_un_05 = Shock_5$simulation$nben_h_un
nl_g_05 = Shock_5$simulation$nl_g
nsben_h_05 = Shock_5$simulation$nsben_h
dp_person_05 = Shock_5$simulation$dp_person
u_ds_05 = Shock_5$simulation$u_ds
shock_kuld_05 = Shock_5$simulation$shock_kuld
unemp_05 = Shock_5$simulation$unemp

@@

plot(dp_person_05, col= "red"); lines(dp_person_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(yk_ds_05, col= "red"); lines(yk_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_ds_t_05, col= "red"); lines(wage_ds_t_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(ur_ds_05, col= "red"); lines(ur_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(shock_kuld_05, col= "red"); lines(shock_kuld_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(u_ds_05, col= "red"); lines(u_ds_04, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

```{r}
plot(((yk_ds_05 - yk_ds_bs56) / yk_ds_bs56), col= "blue", xlab= "Year", ylab= "% Change in Gdp", main= "Gdp", ylim= c(-0.001, 0.0015));
lines(((yk_ds_04 - yk_ds_bs4) / yk_ds_bs4), col= "red");
lines(((yk_ds_03 - yk_ds_bs3) / yk_ds_bs3), col= "black");
lines(((yk_ds_02 - yk_ds_bs2) / yk_ds_bs2), col= "orange");
lines(((yk_ds_01 - yk_ds_00) / yk_ds_00), col= "green");
legend("left", legend=c("All channels","Insurance rate channel", "Productivity channel", "Wage channel", "Demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","red", "black","orange", "green"));
grid()

plot(((emp_05 - emp_bs56)*1000), col= "blue", xlab= "Year", ylab= "Change in Employment (people)", main= "Employment");
lines(((emp_03 - emp_bs3)*1000), col= "black");
legend("left", legend=c("All channels","Productivity channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black"));
grid()
```

```{r}
plot((nl_g_05-nl_g_bs56), col= "red")
```

## Scenario 5b sens all

@@

## Scenario 6 new shock

```{r}
# Define add-factor list (defining shock)
constantAdjList6 <- list(

  shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_max_dp_model = TIMESERIES(shock_max_dp_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_6 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList6
                    )
```

yk_ds_06 = Shock_6$simulation$yk_ds
emp_06 = Shock_6$simulation$emp
wage_ds_06 = Shock_6$simulation$wage_ds
ur_ds_06 = Shock_6$simulation$ur_ds
pc_ds_06 = Shock_6$simulation$pc_ds
yd_hk_ds_06 = Shock_6$simulation$yd_hk_ds
pconk_ds_06 = Shock_6$simulation$pconk_ds
komp_r_06 = Shock_6$simulation$komp_r
max_dp_06 = Shock_6$simulation$max_dp
nben_h_06 = Shock_6$simulation$nben_h
yd_hk_ds_06 = Shock_6$simulation$yd_hk_ds
ik_06 = Shock_6$simulation$ik
wage_ds_t_06 = Shock_6$simulation$wage_ds_t
nben_h_un_06 = Shock_6$simulation$nben_h_un
nl_g_06 = Shock_6$simulation$nl_g
nsben_h_06 = Shock_6$simulation$nsben_h

dp_person_06 = Shock_6$simulation$dp_person
prod_06 = Shock_6$simulation$prod

```{r}
plot(max_dp_06, col= "red"); lines(max_dp_bs56, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(dp_person_06, col= "red"); lines(dp_person_bs56, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(prod_06, col= "red"); lines(prod_bs56, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

```{r}
plot((emp_06-emp_bs56)*1000, col= "red")
```

## Scenario 6b new shock

```{r}
# Define add-factor list (defining shock)
constantAdjList6b <- list(

  shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_max_dp_model = TIMESERIES(shock_max_dp_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_6b <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList6b
                    )
```

>>>>

  shock_1_model  = TIMESERIES(c(shock_1_model ),   
                           START=c(2005,2),FREQ=4),
  shock_2_model  = TIMESERIES(c(shock_2_model ),   
                           START=c(2005,2),FREQ=4),
  shock_3_model  = TIMESERIES(c(shock_3_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
   pf_shock = TIMESERIES(c(pf_shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
  pm_ds_shock = TIMESERIES(c(pm_ds_shock),   
                        START=c(2005,2),FREQ=4),
  iloan_shock = TIMESERIES(c(iloan_shock),   
                        START=c(2005,2),FREQ=4),
  idep_shock = TIMESERIES(c(idep_shock),   
                        START=c(2005,2),FREQ=4),
   ibd_shock = TIMESERIES(c(ibd_shock),   
                        START=c(2005,2),FREQ=4),
  iboa_shock = TIMESERIES(c(iboa_shock),   
                        START=c(2005,2),FREQ=4),
   tax_rate1_shock = TIMESERIES(c(tax_rate1_shock),   
                        START=c(2005,2),FREQ=4),
  wage_gap = TIMESERIES(c(wage_gap),   
                        START=c(2006,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
  wage_ds_tt = TIMESERIES(c(wage_ds_tt),   
                        START=c(2006,1),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4),
   kont_h_ratio = TIMESERIES(c(kont_h_dp_person),   
                        START=c(2005,2),FREQ=4),
     kont_h = TIMESERIES(c(kont_h),   
                        START=c(2005,2),FREQ=4),
    prod_ds_shock = TIMESERIES(c(prod_ds),   
                        START=c(2005,2),FREQ=4),
  d_2007q4 = TIMESERIES(c(d_2007q4),   
                        START=c(2005,2),FREQ=4),
  lf_test = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  shock_lf_model = TIMESERIES(c(shock_lf_model),   
                        START=c(2005,2),FREQ=4),
  emp_old = TIMESERIES(c(emp),   
                        START=c(2005,2),FREQ=4),
  emp_sens = TIMESERIES(c(emp),   
                        START=c(2005,2),FREQ=4),
   prod_ds_sens = TIMESERIES(c(prod_ds),   
                        START=c(2005,2),FREQ=4),
    xk_ds_used = TIMESERIES(c(xk_ds),   
                        START=c(2005,2),FREQ=4),
  xk_ds_disc = TIMESERIES(c(xk_ds),   
                        START=c(2005,2),FREQ=4)
  )
```

@@

```{r}
plot(prod_bs3, col= "green"); lines(prod, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()
```

@@

## Baseline Scenario 5

@@

## Baseline Scenario 5b Sens all

@@

## Baseline Scenario 7 all but prod and wage

@@

```{r}
plot(part_000, col= "red"); lines(part_bs1, col = "blue");
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("red", "blue")); 
grid()
```

@@

```{r}
plot(part_01, col= "red"); lines(part_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

yk_ds_02 = Shock_2$simulation$yk_ds
emp_02 = Shock_2$simulation$emp
wage_ds_02 = Shock_2$simulation$wage_ds
ur_ds_02 = Shock_2$simulation$ur_ds
pc_ds_02 = Shock_2$simulation$pc_ds
yd_hk_ds_02 = Shock_2$simulation$yd_hk_ds
pconk_ds_02 = Shock_2$simulation$pconk_ds
komp_r_02 = Shock_2$simulation$komp_r
max_dp_02 = Shock_2$simulation$max_dp
nben_h_02 = Shock_2$simulation$nben_h
yd_hk_ds_02 = Shock_2$simulation$yd_hk_ds
ik_02 = Shock_2$simulation$ik
wage_ds_t_02 = Shock_2$simulation$wage_ds_t
nben_h_un_02 = Shock_2$simulation$nben_h_un
nl_g_02 = Shock_2$simulation$nl_g
nsben_h_02 = Shock_2$simulation$nsben_h
dp_person_02 = Shock_2$simulation$dp_person
xk_ds_02 = Shock_2$simulation$xk_ds
mk_ds_02 = Shock_2$simulation$mk_ds
ik_02 = Shock_2$simulation$ik
rer_02 = Shock_2$simulation$rer
ps_ds_02 = Shock_2$simulation$ps_ds
i_bd_nfc_k_ds_02 = Shock_2$simulation$i_bd_nfc_k_ds
yd1_hk_ds_02 = Shock_2$simulation$yd1_hk_ds
yd2a_hk_ds_02 = Shock_2$simulation$yd2a_hk_ds
yd2b_hk_02 = Shock_2$simulation$yd2b_hk
i_equip_nfc_k_ds_02 = Shock_2$simulation$i_equip_nfc_k_ds
u_ds_02 = Shock_2$simulation$u_ds
wage_gap1_02 = Shock_2$simulation$wage_gap1
gk_02 = Shock_2$simulation$gk
kont_h_ratio_02 = Shock_2$simulation$kont_h_ratio
lf_02 = Shock_2$simulation$lf
wage_gap_02 = Shock_2$simulation$wage_gap
max_gap_02 = Shock_2$simulation$max_gap
unemp_02 = Shock_2$simulation$unemp
inflation_02 = Shock_2$simulation$inflation
prod_02 = Shock_2$simulation$prod
net_balance_02 = xk_ds_02 - mk_ds_02
```

```{r}
plot(wage_ds_02, col= "red"); lines(wage_ds_bs2, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

@@

```{r}
plot((unemp_02-unemp_bs2)*1000, col= "red")
```

@@

#Elasticity on wage
pr_change_wage_ds_02/pr_change_komp_r_02
#Elasticity on unemployment
pr_change_unemp_02/pr_change_komp_r_02
```

@@

```{r}
# Define add-factor list (defining shock)
constantAdjList_3 <- list(
  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2006,3),  FREQ='Q')
)

@@

```{r}
plot(yk_ds_03, col= "red"); lines(yk_ds_bs3, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

@@

## Scenario 5 ALL

@@

```{r}
###Gengivelse af stød til model
yk_ds_05 = Shock_5$simulation$yk_ds
emp_05 = Shock_5$simulation$emp
wage_ds_05= Shock_5$simulation$wage_ds
ur_ds_05 = Shock_5$simulation$ur_ds
pc_ds_05 = Shock_5$simulation$pc_ds
yd_hk_ds_05 = Shock_5$simulation$yd_hk_ds
pconk_ds_05 = Shock_5$simulation$pconk_ds
komp_r_05 = Shock_5$simulation$komp_r
max_dp_05 = Shock_5$simulation$max_dp
nben_h_05 = Shock_5$simulation$nben_h
yd_hk_ds_05 = Shock_5$simulation$yd_hk_ds
ik_05 = Shock_5$simulation$ik
wage_ds_t_05 = Shock_5$simulation$wage_ds_t
nben_h_un_05 = Shock_5$simulation$nben_h_un
nl_g_05 = Shock_5$simulation$nl_g
nsben_h_05 = Shock_5$simulation$nsben_h
dp_person_05 = Shock_5$simulation$dp_person
u_ds_05 = Shock_5$simulation$u_ds
shock_kuld_05 = Shock_5$simulation$shock_kuld
unemp_05 = Shock_5$simulation$unemp
```

@@

```{r}
plot(((yk_ds_05 - yk_ds_bs56) / yk_ds_bs56)*100, col= "blue", xlab= "Year", ylab= "% Change in Gdp", main= "Gdp", ylim= c(-0.1, 0.15));
lines(((yk_ds_04 - yk_ds_bs4) / yk_ds_bs4)*100, col= "red");
lines(((yk_ds_03 - yk_ds_bs3) / yk_ds_bs3)*100, col= "black");
lines(((yk_ds_02 - yk_ds_bs2) / yk_ds_bs2)*100, col= "orange");
lines(((yk_ds_01 - yk_ds_00) / yk_ds_00)*100, col= "green");
legend("left", legend=c("All channels","Insurance rate channel", "Productivity channel", "Wage channel", "Demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","red", "black","orange", "green"));
grid()

plot(((unemp_05 - unemp_bs56)*1000), col= "blue", xlab= "Year", ylab= "Change in Unemployment (people)", main= "Unemployment", ylim= c(0,25000));
lines(((unemp_03 - unemp_bs3)*1000), col= "black");
legend("left", legend=c("All channels","Productivity channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black"));
grid()
```

## Scenario 5b sens ALL

@@
